---
title: "OLTP Mongo"
author: "VadimTk"
date: "Jun, 2016"
--output: html_document
output:
  md_document:
    variant: markdown_github

---

```{r setup, include=FALSE}
library(svglite)
library(extrafont)
font_import()
knitr::opts_chunk$set(echo = TRUE,dev="png", 
               dev.args=list(type="cairo-png"),
               dpi=300)
library("RMySQL")
library(stringr)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(knitr)

tm<-theme(legend.position="right",
          strip.background = element_rect(colour="red", fill="#CCCCFF"),
          text=element_text(family="Garamond",size=14))

guides(colour = guide_legend(override.aes = list(size=4)))


cons <- dbListConnections(MySQL())
for(con in cons)
    dbDisconnect(con)
con <- dbConnect(MySQL(), user="sbtest", dbname="benchmarks", host="10.20.2.4")

```

# Percona Server for MongoDB 3.2

## Setup

* Client (sysbench-mongodb) and server are on different servers, connected via 10Gb network. 
* CPU: 56 logical CPU threads servers Intel(R) Xeon(R) CPU E5-2683 v3 @ 2.00GHz
* sysbench 8 tables x 60mln rows, uniform distribution
* OS: Ubuntu 16.04 (Xenial Xerus)
* Kernel 4.4.0-21-generic
* Storage devices
  * Samsung SM863 SATA SSD, single device, with ext4 filesystem
  * Samsung 850 PRO SATA SSD, single device, with ext4 filesystem
  * Samsung PM 1725 NVMe SSD, single device

# Results


=============

# Read-only

## RO, cachesize vary
### Samsung 850

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-ONLY samsung 850"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RO-memory-disk-sam850" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

pavg = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, AVG(tps), AVG(rt) 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RO-memory-disk-sam850" AND threads=112 GROUP BY engine,cachesize
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=engine))

m+geom_jitter(size=1)+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  theme(axis.text.x=element_text(size=8,angle = 90, hjust = 1))

ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RO-cache.png", width=12, height=8)

```

## RO, threads vary
### Samsung 850

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-ONLY samsung 850"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RO-memory-disk-sam850" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter(size=1)+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")+
  facet_wrap(~cachesize,labeller = label_both)+
  theme(axis.text.x=element_text(size=12,angle = 90, hjust = 1))

ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RO-threads.png", width=12, height=8)

```

## RO, cachesize vary
### Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-ONLY / samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RO-memory-disk-sam863" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+tm+
  scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  theme(axis.text.x=element_text(size=8,angle = 90, hjust = 1))

ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RO-cache.png", width=12, height=8)


```

## RO, Threads 1-1000 in memory (cachesize 200GB)
### Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-ONLY in-memory SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_ro_threads_sam863_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RO-threads.png", width=12, height=8)


```

# Read-Writes 

## RW, cachesize vary
### Samsung 850

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-WRITE samsung 850"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RW-memory-disk-sam850" AND threads in 
                    (SELECT threads FROM sb_mongo_results WHERE runsign="OLTP-RW-memory-disk-sam850" GROUP BY threads HAVING COUNT(*)>20)
                 ' )

m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  theme(axis.text.x=element_text(size=8,angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RW-cache-jitter.png", width=12, height=8)


m+geom_boxplot()+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+
  scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  tm+theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RW-cache-boxplot.png", width=12, height=8)

```

## RW, cachesize vary
### Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-WRITE samsung 863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="OLTP-RW-memory-disk-sam863" AND threads in 
                    (SELECT threads FROM sb_mongo_results WHERE runsign="OLTP-RW-memory-disk-sam850" GROUP BY threads HAVING COUNT(*)>20)
                 ' )

m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  theme(axis.text.x=element_text(size=8,angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-cache-jitter.png", width=12, height=8)


m+geom_boxplot()+expand_limits(y=0)+
  labs(x="cachesize, GB",y="Throughput, tps",title=title)+
  scale_color_tableau(name="Engine")+
  facet_wrap(~threads,labeller = label_both)+
  tm+theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-cache-boxplot.png", width=12, height=8)

```



# Read-Write, threads

## RW, Threads 1-1000 in memory (cachesize 200GB)

### Samsung 850

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-WRITE in memory / samsung 850 Pro"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_sam850_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RW-threads-scale.png", width=12, height=8)

m <- ggplot(subset(p2,threads==112), aes(x=as.numeric(sec),y=as.numeric(tps),color=engine))

m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="--- time, sec --->",y="Throughput, tps",title="sysbench OLTP READ-WRITE in memory / 112 threads /samsung 850 Pro")+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RW-threads-scale-112threads.png", width=12, height=8)

```
### Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-WRITE in memory / samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_sam863_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-threads-scale.png", width=12, height=8)

```
### Samsung PM1725

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "[network] sysbench OLTP READ-WRITE in memory / samsung PM1725"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_pm1725_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/pm1725-RW-threads-scale.png", width=12, height=8)

```

### Samsung storage

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE in memory"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, storage,tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign IN ("oltp_rw_threads_pm1725_network","oltp_rw_threads_sam850_network","oltp_rw_threads_sam863_network") AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

p2$storage_f = factor(p2$storage, levels=c('sam850','sam863','pm1725'))

m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+facet_wrap(~storage_f)+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/storage-RW-threads-scale.png", width=12, height=8)

```
## RW, Threads 1-1000 io-bound (cachesize 20GB)
### Samsung 850

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE io-bound / samsung 850 Pro"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_cache20G_sam850_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>20)
                 ' )

m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam850-RW-io-threads-scale.png", width=12, height=8)


```

### Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE iobound / samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_cache20G_sam863_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-io-threads-scale.png", width=12, height=8)

```

### RW, Threads 112 io bound (cachesize 20GB)
* Samsung 863

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE iobound / samsung SM863 / 112 threads"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_cache20G_sam863_network" AND threads=112 
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.numeric(sec),y=as.numeric(tps),color=engine))

m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="--- time, sec [10 sec intervals] --->",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-io-threads-112t.png", width=12, height=8)


```

### Samsung 863 - syncdelay 60/600

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE iobound / samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt,
                json_unquote(json_extract(jrunid,"$.syncdelay")) syncdelay 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_longrun_cache20G_sam863_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

m <- ggplot(p2, aes(x=as.numeric(sec),y=as.numeric(tps),color=syncdelay))

m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="--- time, sec --->",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="syncdelay")+facet_grid(syncdelay~.,labeller = label_both)
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-io-sync-delay.png", width=12, height=8)


m <- ggplot(p2, aes(x=as.factor(syncdelay),y=as.numeric(tps),color=syncdelay))

m+geom_boxplot()+expand_limits(y=0)+
  labs(x="syncdelay",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="syncdelay")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/sam863-RW-io-sync-delay-boxplot.png", width=12, height=8)


```
## RW, Threads 1-300 io-bound (cachesize 20GB)
### Samsung pm1725

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE io-bound / samsung PM1725"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_threads_cache20G_pm1725_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>20)
                 ' )

flevels <- levels(as.factor(p2$cachesize))

m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))

ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/pm1725-RW-io-threads-scale.png", width=12, height=8)


m+geom_boxplot()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))

```



### Samsung storage

```{r , echo=FALSE, fig.height=8, fig.width=10, warning=FALSE}

title <- "sysbench OLTP READ-WRITE iobound"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, storage,tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign IN ("oltp_rw_threads_cache20G_pm1725_network","oltp_rw_threads_cache20G_sam850_network","oltp_rw_threads_cache20G_sam863_network") AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

p2$storage_f = factor(p2$storage, levels=c('sam850','sam863','pm1725'))

m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+
  tm+scale_color_tableau(name="Engine")+
  theme(axis.text.x=element_text(size=8, angle = 90, hjust = 1))+
  facet_wrap(~storage_f)
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/storage-RW-io-threads-scale.png", width=12, height=8)

```




* Charts examples

```{r, eval=FALSE, fig.height=8, fig.width=10, warning=FALSE, include=FALSE}

title <- "[network] sysbench OLTP READ-WRITE in memory / samsung 850 Pro"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt, json_unquote(json_extract(jrunid,"$.syncdelay")) syncdelay 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_rw_longwrite_sam850_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )


title <- "[network] sysbench OLTP READ-WRITE in memory"
p1 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, storage,tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign IN ("oltp_rw_threads_pm1725_network","oltp_rw_threads_sam850_network","oltp_rw_threads_sam863_network") AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(threads),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="Threads",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")+facet_wrap(~storage)

p2 <- subset(p1,storage=="sam863" & threads==112 & engine=="wt")

m <- ggplot(p2, aes(x=sec,y=as.numeric(tps),color=engine))
m+geom_point()+expand_limits(y=0)+
  labs(x="--- Time, sec, resolution 10 sec ---->",y="Throughput, tps",title="scatterplot")+tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/scatterplot.png", width=12, height=8)

m <- ggplot(p2, aes(x=sec,y=as.numeric(tps),color=engine))
m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="--- Time, sec, resolution 10 sec ---->",y="Throughput, tps",title="scatterplot + line")+tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/scatterplot-line.png", width=13, height=8)

m <- ggplot(p2, aes(x=engine,y=as.numeric(tps),color=engine))
m+geom_jitter()+expand_limits(y=0)+
  labs(x="engine",y="Throughput, tps",title="jitter plot")+tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/jitter.png", width=6, height=8)

m <- ggplot(p2, aes(x=engine,y=as.numeric(tps),color=engine))
m+geom_boxplot()+expand_limits(y=0)+
  labs(x="engine",y="Throughput, tps",title="boxplot")+tm+scale_color_tableau(name="Engine")
ggsave(file="/Users/vadim/Google Drive/CTO Lab/img/boxplot.png", width=6, height=8)


m <- ggplot(subset(p2,syncdelay==60), aes(x=syncdelay,y=as.numeric(tps),color=syncdelay))
m+geom_jitter()+expand_limits(y=0)+
  labs(x="syncdelay",y="Throughput, tps",title="jitter plot")+tm+scale_color_tableau(name="syncdelay")

m <- ggplot(p2, aes(x=as.numeric(sec),y=as.numeric(tps),color=syncdelay))
m+geom_point()+geom_line()+expand_limits(y=0)+
  labs(x="--- Time, sec, resolution 10 sec ---->",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="syncdelay")

m <- ggplot(p2, aes(x=as.factor(syncdelay),y=as.numeric(tps),color=syncdelay))

m+geom_boxplot()+expand_limits(y=0)+
  labs(x="syncdelay 60/600",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="syncdelay")+tm
 
```


*RO, memory scale

```{r, eval=FALSE, fig.height=8, fig.width=10, warning=FALSE, include=FALSE}
title <- "[network] sysbench OLTP Read-Only  samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt 
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_ro_memory_sam863_network" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))
m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=engine))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="CacheSize, GB",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")


```

*RocksDB, compession

```{r, eval=FALSE, fig.height=8, fig.width=10, warning=FALSE, include=FALSE}
title <- "[network] sysbench OLTP Read-Only  samsung SM863"
p2 = dbGetQuery( con,'SELECT sec,sr.runid runidfull, sr.threads, cachesize, engine, workload, tps, rt, json_unquote(json_extract(jrunid,"$.compression")) compr
                 FROM sb_mongo_results sr 
                 WHERE runsign="oltp_ro_compression_sam863_local" AND threads in 
                    (SELECT threads FROM sb_mongo_results GROUP BY threads HAVING COUNT(*)>10)
                 ' )

flevels <- levels(as.factor(p2$cachesize))

m <- ggplot(p2, aes(x=as.factor(cachesize),y=as.numeric(tps),color=compr))

m+geom_jitter()+expand_limits(y=0)+
  labs(x="CacheSize, GB",y="Throughput, tps",title=title)+tm+scale_color_tableau(name="Engine")+facet_wrap(~threads)


```
